Area maximisation in continuous time

### 2013-01-11 Notes/ContTime.tex
used global preamble
notes for model of VOR expt

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
% Preamble:
\usepackage{a4wide}
\usepackage[centertags]{amsmath}
%\usepackage{ams} for finding documentation only
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage[sort&compress,numbers]{natbib}
%\usepackage{citeB}
\usepackage{ifpdf}
%\usepackage{graphicx}
%\usepackage{graphics} for finding documentation only
%\usepackage{xcolor}
%\usepackage{pgf}
\ifpdf
\usepackage[pdftex,bookmarks,bookmarksopen,pdfstartview=FitH]{hyperref}
\else
\usepackage[hypertex]{hyperref}
%\DeclareGraphicsRule{.png}{eps}{.bb}{}
\fi
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz2pt % Don't report over-full h-boxes if over-edge is small
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{mydefs.tex}
\input{newsymb.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\eq}{\mathbf{p}^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
% ----------------------------------------------------------------
\usepackage{amsthm}
\newtheoremstyle{sldefinition}%
  {3pt}%space above
  {3pt}%space below
  {}%body font
  {}%indent amount
  {\bfseries}%theorem head font
  {}%theorem head punctuation
  {\newline}%space after head
  {\thmname{#1}\thmnumber{ #2}:{\bfseries\thmnote{ #3}}}%head spec
\newtheoremstyle{slplain}%
  {3pt}%space above
  {3pt}%space below
  {}%body font
  {}%indent amount
  {\bfseries}%theorem head font
  {}%theorem head punctuation
  {\newline}%space after head
  {\thmname{#1}\thmnumber{ #2}{\bfseries\thmnote{ (#3)}}: }%head spec
%
\theoremstyle{slplain}
\newtheorem{thm}{Theorem}
\newtheorem{cor}[thm]{Corollary}
%
\theoremstyle{sldefinition}
\newtheorem{defn}{Definition}
%
\theoremstyle{remark}
\newtheorem*{notn}{Notation}
\newtheorem*{rem}{Remark}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Area maximisation in continuous time}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

\subsection{Derivatives \wrt $\W^\pm$}\label{sec:deriv}

@@

\subsubsection{Increasing $c_k$}\label{sec:areacoeffincr}

@@

\subsection{Differences in $c_k$'s}\label{sec:areacoeffdiff}

@@

\subsection{Derivatives \wrt $\fptb$}\label{sec:derivT}

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\eq}{\mathbf{p}^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Area maximisation in continuous time}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

\subsection{Derivatives \wrt \texorpdfstring{$\W^\pm$}{W+/-}}\label{sec:deriv}

@@

\subsubsection{Increasing \texorpdfstring{$c_k$}{c(k)}}\label{sec:areacoeffincr}

@@

\subsection{Differences in \texorpdfstring{$c_k$}{c(k)}'s}\label{sec:areacoeffdiff}

@@

\subsection{Derivatives \wrt \texorpdfstring{$\fptb$}{T}}\label{sec:derivT}
